New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-08-09 paper/answer_rev_1.tex
wip

\documentclass[letterpaper]{letter}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{siunitx}
\sisetup{group-separator = {,}}

\usepackage{multirow}

%\journal{EJOR}

\usepackage[mathscr]{eucal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Co}{\mathbb{Co}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}
\newcommand{\bigO}{\mathscr{O}}
\newtheorem{thm}{Theorem}
\newtheorem{prp}{Proposition}
\newtheorem{lem}{Lemma}
%\newdefinition{rmk}{Remark}
%\newdefinition{definition}{Definition}
%\newproof{pf}{Proof}
%\renewcommand\qedsymbol{$\blacksquare$}

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}
\signature{Danilo Tedeschi}

\begin{document}

		%\title{Cover Letter}
		%\maketitle

		\begin{letter}{}

			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.

		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}
		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

\end{document}

>>>>

		%\title{Answer to Reviewer #1}
		%\maketitle

\section*{Answer to reviewer \# 1}
		%\opening{Answer to Reviewer \#1}

		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		First, thanks for dedicating your time to revise our work, it is a great honor for us to continue to improve our work with your help.

		Following we provide answers to each one of the comments you have given us:

		\textbf{Comment \#1:} ``The authors indicate that `it is fair to say that PMCLP with elliptical coverage has not been vastly studied as only two articles have been found on it.' I would like the authors to expand on this. In particular, addressing under which real-world conditions the elliptical shape is the ideal shape to model coverage. The paper is technically correct, and it was interesting to follow the development of the model; however, the authors did not really intent to connect to a real-world application where elliptical coverage is needed or desired. Maybe there's little research because there's no interest on the particular problem? In the absence of a practical application motivating the extension to ellipses, this paper has limited interest."

		We agree with that a real-world application connection was missing in our work. We believe that after the changes we made to address this issue, it is clear that the problems explored in our paper is not of limited interested.

		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

		``In the real world, this problem comes up when a telecommunications company has to buy and
		place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming
		profit maximization. More details about the applications of PMCLP can be found in [5], which also
		ponders about the practical importance of considering the PMCLP with elliptical coverage."

		This change can be found in page 3 of the manuscript. Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.

		\textbf{Comment \#2:} ``I also would like the authors to discuss potential extensions, specially if there's evidence that the elliptical shape is indeed useful to model facility coverage. Given fixed coverage areas, is it possible to allow minor and major axes to be decision variables to determine with shapes cover a particular space better? The aspect ratio and how elongated or circular the ellipses are at the final solution given different space densities might be an interesting issue to explore, rather than fixing the shape of the ellipses from the onset."

		Thanks for this idea of extension to our problem, we think it is very interesting, and we did devote some time to think about it.
		We believe that there is not a trivial adaptation to any of methods that would make it possible to work for this variation of the problem; at least for us it seems like it would require extensive work. 
		We added a paragraph to the conclusion to pass this idea on, giving it as a suggestion for future works on the subject:

		``We believe
		that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of
		MCE and MCER; having only one additional decision variable –the major or minor axis– might
		still allow a similar model to be employed, even though extensive work would be necessary to
		adapt, somehow, the theory developed for this version, especially of MCER."

	%	\closing{On behalf of the authors and with our best regards,}
			%\end{letter}

### 2020-08-09 paper/answer_rev_2.tex
wip

		\begin{letter}{}

		\opening{Answer to Reviewer \#2}
		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.

		The changes we have made to the text are highlighted by different colors. 
		\begin{itemize}
			\item The {\color{blue} blue} highlights are small corrections that were pointed out by the board that revised the dissertation from which this paper originated.

			\item The {\color{Red} red} highlights are corrections concerning the points made by reviewer \#1.

			\item The {\color{Green} green} highlights are corrections concerning the points made by reviewer \#2.

			\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
		\end{itemize}

		Following we provide answers to each one of your comments:

@@

		We address this issued by adding a paragraph to the end of our introduction, please see page 3 and 4.

		\textbf{Comment \#2:} ``In my opinion "fixed shape" ellipses should be replaced by "fixed shape parameters" ellipses, or ellipses with the given semi-major and semi-minor axes. Alternately the term "fixed shape" ellipses should be explained."

		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote some pieces of text were this was being used:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

			\item In the ``Introduction" section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."

@@

		\textbf{Comment \#3:} ``Please, extend the description of practical applications."
		We address this issued by re-writing a piece of our introduction. The changes are in the ``Introduction" section (page 3). We decided to make a brief comment about the real-world applications of the problem and cite another work that explores this with greater detail. Also, because of the changes made to fit this comment, we ended up rewriting the next paragraph.

		\textbf{Comment \#4:} ``The literature review in Introduction is a bit limited and should to be extended analyzing more approaches and references on the subject. It can be expected that beginning from the first publication [8] in 1984 a reasonable number of references on the subject have been published. See, e.g. papers: (...)"

		This issued is addressed in the ``Introduction" section on page 2. We agree with you that the literature review needed improvement, this is the sum-up of the changes we made:

		\begin{itemize}
			\item We add a citation to ``H Younies and G O Wesolowsky. Planar maximal covering location problem under block norm distance measure". This shows another example of versions of PMCLP other than the classical one using Euclidean norm.
			\item We add a citation to the survey paper: ``Alan T. Murray. Maximal coverage location problem: Impacts, significance, and evolution.". Instead of giving an extensive review, we use a common practice of citing a survey paper. 
		\end{itemize}

		Also, regarding the possible works that we could cite in our paper suggested by you, besides the PHD thesis of Daoqin Tong, who has some of his works cited in the above survey, we think that the other suggested papers seem not to be that closely related to our problem.

@@

		We addressed this issue in section 8.2 ``New instances" (page 19). Now, we hope it is clear that the critical parameter is the number of ellipses.

@@

		We are using the same definition of PMCLP used in the several works we cited, maybe you could elaborate more why this seems natural?

@@

		Our algorithm does not support this constraint, and we do not see any trivial modification that could make it do.

		Please see: \href{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf}{https://github.com/danft/masters-thesis/raw/master/paper/figures/answer-to-reviewer-2.pdf} for a counter-example of how our algorithm fails for this constraint. That is, there are non-overlapping solutions, however, it is possible to see that our algorithm would fail to find any -- try it yourself, notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}

>>>>

%		\begin{letter}{}
%
%		\opening{Answer to Reviewer \#2}
		%	\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		\section*{Answer to reviewer \# 2}
		First, thanks for dedicating your time to revise our work. We found every one of the points made of great importance for us to achieve a top quality paper.

		Following we provide answers to each one of the comments you have given us:

@@

		We address this issued by adding a paragraph to the end of our Introduction:

		``This paper is organized as follows. Section 2 presents the definitions of both problems and
		3introduces some notations used throughout the rest of the work. An algorithm for MCE is developed
		in Section 3, and an algorithm for MCER in Section 5 with the observation that its development
		depends on a subproblem whose algorithm is developed in Section 4. Improvements suggestions to
		the implementations are given in Section 6 while the implementation details are given in Section 7.
		Numerical results are presented and analyzed in Section 8. Finally, a conclusion is given in Section 9."

		This paragraph can be found in the manuscript in pages 3 and 4.

		\textbf{Comment \#2:} ``In my opinion `fixed shape' ellipses should be replaced by `fixed shape parameters' ellipses, or ellipses with the given semi-major and semi-minor axes. Alternately the term `fixed shape' ellipses should be explained."

		We agree that using ``fixed shape" without clearly defining what it is can be confusing to the reader. To address this issue we rewrote the pieces of text where this was being used:
		\begin{itemize}
			\item In the first paragraph of the abstract (page 2), we used the term ``given their major and minor axis" to better convey the same idea.

			\item In the Introduction section (page 3), we changed the description of our problem to: ``(...) each ellipse is defined to have fixed major and minor axis and an undefined location (...)."

@@

		\textbf{Comment \#3:} ``Please, extend the description of practical applications."

		We address this issued by adding a new paragraph to our Introduction citing the work ``\textit{Mustafa S. Canbolat and Michael von Massow. Planar maximal covering with ellipses.}", which covers with great detail the practical applications of the problems studied in our work:

		``In the real world, this problem comes up when a telecommunications company has to buy and
		place antennas over a region to distribute a signal to a population, not necessarily everyone, aiming
		profit maximization. More details about the applications of PMCLP can be found in [5], which also
		ponders about the practical importance of considering the PMCLP with elliptical coverage."

		This change can be found in page 3 of the manuscript. Also, to better fit this addition, we had to modify the paragraph after the added one; we do not display it here because it is not relevant to this comment.

		\textbf{Comment \#4:} ``The literature review in Introduction is a bit limited and should to be extended analyzing more approaches and references on the subject. It can be expected that beginning from the first publication [8] in 1984 a reasonable number of references on the subject have been published. See, e.g. papers:

		'A Combinatorial Maximum Cover Approach to 2D Translational Geometric Covering' by K. Daniels A. Mathur R. Grinde

		'Covering a polygonal region by rectangles' by G. Scheithauer, Y. Stoyan, T. Romanova, A. Krivulya

		'Translational polygon containment and minimal enclosure' using mathematical programming
		by V.J. Milenkovic , K. Daniels

		and references in 2007 PhD thesis of Daoqin Tong from the Ohio State University."

		This issued is addressed in the Introduction section on page 2. We agree with you that the literature review needed improvement, and we believe that we were able to improve on that regard with the following changes:

		\begin{itemize}
			\item We added a citation to ``H Younies and G O Wesolowsky. Planar maximal covering location problem under block norm distance measure". This shows another example of versions of PMCLP other than the classical one using Euclidean norm.
			\item We added a citation to the survey paper: ``Alan T. Murray. Maximal coverage location problem: Impacts, significance, and evolution.". Instead of giving an extensive review, we use a common practice of citing a survey paper. 
		\end{itemize}

	Now, after these additions, the piece of our Introduction doing literature review of PMCLP is as follows:

	``A continuous extension of MCLP, where the facility and demand sets are located on the plane and coverage is determined by a norm function, was introduced in [8] and named Planar Maximal	Covering Location Problem (PMCLP) following the advances on covering location problems on the	plane that were being made at the time.

	PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage
	defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in [4], for example, the demand set is defined as a set of rectangles; and in [20], a version of PMCLP where coverage is determined using block norms is studied. For a more comprehensive review on PMCLP and MCLP, please see [15].

	In our work, because of the similarities with the problems studied by us, we are particularly interested in the Euclidean PMCLP defined with coverage being determined by the Euclidean norm.	In [8], a method for this version of PMCLP was developed following the demonstration of a theorem,	which showed that a finite set of locations could be constructed to contain at least one optimal	solution transforming PMCLP into a combinatorial optimization problem."

	We did consider the list of suggested works we could look at to improve our literature review you have given us, however, even though we think they are great suggestions, we decided to cite two works we were more familiar with, also with the intention of not extending this part of the Introduction too much.
	It is worth mentioning though, that some works of Daoqin Tong are cited in the survey paper we are using.

@@

		We addressed this issue in section 8.2 ``New instances" (page 19):

		``We were able to run experiments with up to 700 demand points; however, it is clear that the number of ellipses is the critical parameter of both algorithms, as even for small demand sets, we could not go over 7 ellipses."

@@

		Thanks for this comment, we, too, think that depending on the viewpoint, considering the weight of each point to be a function which depends on the set of ellipses covering is more natural. We believe that our methods could be trivially adapted to work with this different definition, however, we also think that we have to ponder about doing this change because this is not the traditional definition of any other PMCLP we have based our developments on; meaning that we would have to have a strong motive for this not to look like an arbitrary change.

@@

		Thanks for the great question, we thought a lot about this, and we came up with some arguments to show you what happens if we add this constraint to our problem.

		First, for an example of covering without overlapping, please see the paper ``Covering point sets with two disjoint disks or squares" by Cabello, S., Díaz Báñez, J.M., Seara, C., Sellarès, J.A., Urrutia, J., Ventura, I.

		This work deals with the problem of covering points using two Euclidean disks with the constraint of no overlapping being allowed. This article is cited by a work we are citing in our Introduction: ``Covering many or few points with unit disks." by Mark de Berg, Sergio Cabello, and Sariel Har-Peled. 
		This work develops an algorithm for the overlap-allowed covering of points by multiple Euclidean disks. In its Introduction, the authors cite the previous work that does not allow overlap saying: ``This condition changes the problem significantly, because now issues related to packing problems arise". 
		Based on this, we are safe to say that we should expect that adding a no-overlap constraint would change our problem significantly too.

		The way our methods work is to look for solutions with points on the ellipses, this type of solution is not favorable when we have this constraint as, for example, see the counter-example in this figure:

		\includegraphics[scale=.6]{figures/answer-to-reviewer-2}

		It is possible to see that there are non-overlapping solutions, however, our algorithm would fail to find any. Notice that moving the ellipse with no points on its coverage region's border in order to put at least two points on it would cause overlap.

		We believe methods for the problems with this additional constraint would have to come from a different base idea than ours do.

	%	\closing{On behalf of the authors and with our best regards,}
	%		\end{letter}

### 2020-08-09 paper/comments_to_reviewers.tex
wip

\documentclass[letterpaper]{letter}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

@@

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}
\signature{Danilo Tedeschi}

\begin{document}
\begin{letter}{Comments to reviewers}
			\opening{Dear Steffen Rebennack\\Editor of EJOR}

@@

			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own. These modifications were mostly suggestions given by the board that reviewed the dissertation from which this paper derived. In the text, we annoted these changes with the color {\color{blue}blue}.

@@

			Please see in the next pages the answers to both reviewers.

			\closing{On behalf of the authors and with our best regards,}
\end{letter}
	\input{answer_rev_1.tex}
	\input{answer_rev_2.tex}

>>>>

\documentclass{report}

%\usepackage{scrletter}
%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

@@

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}
%\signature{Danilo Tedeschi}

\begin{document}

%\begin{letter}{Comments to reviewers}
%			\opening{Dear Steffen Rebennack\\Editor of EJOR}
%			\date{}

			\noindent Dear Steffen Rebennack,\\ Editor of EJOR
			\\
			\\

@@

			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own in the hopes of improving the manuscript. In the text, we annotated these changes with the color {\color{blue}blue}.

@@

			Please see in the next pages the answers to both reviewers.
			\\
			\\
			\\
			On behalf of the authors and with our best regards,\\
			Danilo Tedeschi.
%\end{letter}
\clearpage
	\input{answer_rev_1.tex}

	\clearpage
	\input{answer_rev_2.tex}
